Efficient Coalition Formation \\ for Web Services

### 2013-07-05 papers/coalition-journal-extension/coalition_journal.tex
Changes

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services in the scenarios where established communities
already exist. Moreover, we analyze the scenarios where
communities are not established yet and web services can form multiple communities. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
simulation results show that our algorithms provide web services
and community owners with applicable and near-optimal decision
making mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11} proposed mechanisms to help
users and services maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
game-theoretic model, the strategies available to a web service
when facing a new community are requesting to join the community,
accepting the master's invitation to join the community, or
refusing the invitation to join. The set of strategies for
communities are inviting the web service or refusing the web
service's join request. Based on their capacity, market share and
reputation, the two players have different set of utilities over
the strategy profiles of the game. The main limits of this game
model are: 1) its consideration of only three quality parameters,
while the other factors are simply ignored; and 2) the
non-consideration of the web services already residing within the
community. The game is only between the community master and the
new web service, and the inputs from all the other members are
simply ignored. The consideration of those inputs is a significant
issue as existing web services can lose utility or payoff because
of the new member, which can results in an unhealthy and unstable
group. The problem comes from the fact that the existing members
should collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

@@

@@

Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration. Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible. We limited our maximum community size by 5 in order to have communities with almost the same size. In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task. However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available. Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm. The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}. Part(c) shows the availability of community from end user point of view. The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase. In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide better visibility,
efficiency, market share and total payoff. There are a number of
proposed mechanisms and models on aggregating web services and
making them cooperate within their communities. However, forming
optimal and stable communities as coalitions to maximize
individual and group efficiency and income has not been addressed
yet. In this paper, we propose an efficient coalition formation
mechanism using cooperative game-theoretic techniques. We propose
a mechanism for community membership requests and selections of
web services in the scenarios where there is interaction between one community and many web services 
and scenarios where web services can join multiple established communities. The ultimate objective is to
develop a mechanism for web services to form stable groups
allowing them to maximize their efficiency and generate
near-optimal (welfare-maximizing) communities. The theoretical and
extensive simulation results show that our algorithms provide web services
and community owners, in real-world like environments, with applicable and near-optimal decision
making mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
game-theoretic model, the strategies available to a web service
when facing a new community are requesting to join the community,
accepting the master's invitation to join the community, or
refusing the invitation to join. The set of strategies for
communities are inviting the web service or refusing the web
service's join request. Based on their capacity, market share and
reputation, the two players have different set of utilities over
the strategy profiles of the game. The main limits of this game
model are: 1) its consideration of only three quality parameters,
while the other factors are simply ignored; and 2) the
non-consideration of the web services already residing within the
community. The game is only between the community master and the
new web service, and the inputs from all the other members are
simply ignored. The consideration of those inputs is a significant
issue as existing web services can lose utility or payoff because
of the new member, which can results in an unhealthy and unstable
group. The problem comes from the fact that the existing members
should collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

@@

In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous 
web services based on coalitional game theory has been introduced. They have proposed an algorithm to 
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise 
that no it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with a lot of emphasis on 
availability metric and also considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task destribution
method, will initially invoke primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
with recent advancement in cloud and hardware infrastructures availability is less of an issue. So the backup web services 
in their model have a very low chance of getting jobs, especially the ones further in chain which is huge waste of web service
capability.

@@

Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration. Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible. We limited our maximum community size by 5 in order to have communities with almost the same size. In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task. However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available. Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm. This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work. The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}. Part(c) shows the availability of community from end user point of view. The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase. In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
